---
title: "Bhaswar Chakma"
output:
  html_document:
    theme: united
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,  message = FALSE, warning = FALSE, fig.width = 10)
```
<script>
   $(document).ready(function() {
     $head = $('#header');
     $head.prepend('<img src=\"pic.jpg\" style=\"float: right;width: 100px;\"/>')
   });
</script>

# {.tabset}

## About

Hi! I am Bhaswar Chakma. Born and raised in [Chittagong Hill Tracts, Bangladesh](https://en.wikipedia.org/wiki/Chittagong_Hill_Tracts), I have been living in Portugal since 2014. I became a Portuguese citizen in April 2021. Outside of work, I love to play the guitar. Here are some of my favorite songs: [Cliffs Of Dover](https://www.youtube.com/watch?v=aiRn3Zlw3Rw); [Always with Me, Always with you](https://www.youtube.com/watch?v=vxeYDEOXsqU); [Electric Gypsy](https://www.youtube.com/watch?v=JIl3V9SdNKY). Let me know if you need more suggestions!
 
Fun Fact: My last name -- [Chakma](https://en.wikipedia.org/wiki/Chakma_people) -- happens to be the name of the indigenous  community that I belong to.

You can reach me at <bhaswar.chakma@outlook.com>.

*Last updated: `r lubridate::today()`*

## CV

Click [here](https://www.dropbox.com/s/d58j65cxk4d9u22/CV-Bhaswar-Chakma.pdf?dl=0).

## Personal Projects

- [toolbox](https://bhaswar-chakma.github.io/toolbox/): I am writing this "book" for future-me! This is kind of quick reference guide. It contains `Python`, `R`, and `SQL` topics. I am adding materials almost every day. Hope to add `Julia` someday!

- [dse](https://bhaswar-chakma.github.io/dse/): This site is about Dhaka Stock Exchange, includes market stats and visualizations. I try to update this site almost every working day!

- [brmlab2021](https://brmlab2021.netlify.app): I built this site for teaching, used this in Spring 2020/21 at CLSBE.



## My Countries

### {.tabset}

```{r}
library(dplyr)
library(ggplot2)
# Data
# https://datatopics.worldbank.org/world-development-indicators/
df_wdi <- WDI::WDI(country=c("PT", "BD"),
         indicator=c(gdp_current_usd = "NY.GDP.MKTP.CD",
                     gdp_growth = "NY.GDP.MKTP.KD.ZG",
                     gdp_pcap_current_usd = "NY.GDP.PCAP.CD",
                     gdp_pcap_growth = "NY.GDP.PCAP.KD.ZG",
                     pop = "SP.POP.TOTL",
                     pop_growth = "SP.POP.GROW",
                     life_exp_total = "SP.DYN.LE00.IN",
                     life_exp_male = "SP.DYN.LE00.MA.IN",
                     life_exp_female = "SP.DYN.LE00.FE.IN",
                     fdi_current_usd = "BX.KLT.DINV.CD.WD",
                     remit_current_usd = "BX.TRF.PWKR.CD.DT",
                     export_current_usd = "NE.EXP.GNFS.CD",
                     export_growth = "NE.EXP.GNFS.KD.ZG",
                     import_current_usd = "NE.IMP.GNFS.CD",
                     import_growth = "NE.IMP.GNFS.KD.ZG"),
         start=1990, end=2020)
```

#### GDP
```{r gdp}

# GDP
df_wdi %>% 
  select(year, country, gdp_current_usd) %>% 
  mutate(gdp = gdp_current_usd/1e9) %>%
  ggplot(aes(x = year, y = gdp, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "$ Billion", title = "GDP (current US$)") +
  theme(legend.title = element_blank())
# GDP Growth
df_wdi %>% 
  select(year, country, gdp_growth) %>% 
  ggplot(aes(x = year, y = gdp_growth, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "%", title = "GDP growth (annual %)") +
  theme(legend.title = element_blank())

# GDP Per Capita 
df_wdi %>% 
  select(year, country, gdp_pcap_current_usd) %>% 
  mutate(gdp_pcap = gdp_pcap_current_usd/1000) %>%
  ggplot(aes(x = year, y = gdp_pcap, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "$ Thousand", title = "GDP per capita (current US$)") +
  theme(legend.title = element_blank())

# GDP Per Capita Growth
df_wdi %>% 
  select(year, country, gdp_pcap_growth) %>% 
  ggplot(aes(x = year, y = gdp_pcap_growth, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "%", title = "GDP per capita growth (annual %)") +
  theme(legend.title = element_blank())

```

#### Population & Life Expectency
```{r}
# Population
df_wdi %>% 
  select(year, country, pop) %>% 
  mutate(popm = pop/1e6) %>%
  ggplot(aes(x = year, y = popm, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "Million", title = "Population, total") +
  theme(legend.title = element_blank())

# Population Growth
df_wdi %>% 
  select(year, country, pop_growth) %>% 
  ggplot(aes(x = year, y = pop_growth, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "%", title = "Population growth (annual %)") +
  theme(legend.title = element_blank())

# Life Expectency Total
df_wdi %>% 
  ggplot(aes(x = year, y = life_exp_total, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "Age", title = "Life expectancy at birth, total (years)") +
  theme(legend.title = element_blank())

# Life Expectancy Female
df_wdi %>% 
  ggplot(aes(x = year, y = life_exp_female, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "Age", title = "Life expectancy at birth, female (years)") +
  theme(legend.title = element_blank())

# Life Expectancy Male
df_wdi %>% 
  ggplot(aes(x = year, y = life_exp_male, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "Age", title = "Life expectancy at birth, male (years)") +
  theme(legend.title = element_blank())
```

#### Trade

```{r trade}
# Export 
df_wdi %>% 
  select(year, country, export_current_usd) %>% 
  mutate(export = export_current_usd/1e9) %>%
  ggplot(aes(x = year, y = export, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "$ Billion", title = "Exports of goods and services (current US$)") +
  theme(legend.title = element_blank())

# Export Growth
df_wdi %>% 
  ggplot(aes(x = year, y = export_growth, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "%", title = "Exports of goods and services (annual % growth)") +
  theme(legend.title = element_blank())

# Import 
df_wdi %>% 
  select(year, country, import_current_usd) %>% 
  mutate(import = import_current_usd/1e9) %>%
  ggplot(aes(x = year, y = import, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "$ Billion", title = "Imports of goods and services (current US$)") +
  theme(legend.title = element_blank())

# Import Growth
df_wdi %>% 
  ggplot(aes(x = year, y = import_growth, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "%", title = "Imports of goods and services (annual % growth)") +
  theme(legend.title = element_blank())

```



#### FDI & Remittance
```{r}
# FDI
df_wdi %>% 
  select(year, country, fdi_current_usd) %>% 
  mutate(fdi = fdi_current_usd/1e9) %>%
  ggplot(aes(x = year, y = fdi, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "$ Billion", title = "Foreign direct investment, net inflows (BoP, current US$)") +
  theme(legend.title = element_blank())
# FDI
df_wdi %>% 
  select(year, country, remit_current_usd) %>% 
  mutate(remit = remit_current_usd/1e9) %>%
  ggplot(aes(x = year, y = remit, color = country)) +
  geom_line(size = 1.5) +
  ggthemes::theme_economist() +
  labs(x = "Year", y = "$ Billion", title = "Personal remittances, received (current US$)") +
  theme(legend.title = element_blank())
```



